Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-04-03 paper/src/paper.tex
tex upd

Providing the computing infrastuctures needed to solve actual complex problems
arising in the various fields of modern society (including climate change,
health, green energy or security) is a strategic challenge. The main pillar of
the answer to this challenge is to build extreme-scale parallel and distributed
platforms. The never-ending race for more computing power and storage capacity does
not only lead to sophisticated specific Exascale platforms, but the objective
of the community is to design efficient sustained Petascale platforms. This
large-scale evolution and the increasing complexity in both architecture and
applications create many scientific and technical problems. Accordingly, system
management software still has a long way to go. The existing job and resource
management software allow to run tens of thousands of jobs on hundreds of thousands
of cores. They are based on robust policies, however, despite their positive
properties such as relative simplicity and prevention of job starvation,
there is still room for improvement. Here, we propose to study how to tune the
ordering of the submission queues in the frame of the classical
EASY-BackFilling family of heuristics using two new online learning approaches
(an approach based on a simulator and an approach using multi-armed bandit).

Most common work in the literature consider \textit{a posteriori} optimization
of a scheduling algorithm on a (actual) data set.  The increasing amount and
diversity of data generated by large scale platforms motivate the community to
study more sophisticated policies that could leverage these data.  During the
last few years, there was an explosion of the number of works at the interface
of HPC and BigData fields, dealing with learning algorithms. Recent
sophisticated approaches developed \textit{ad hoc} supervised machine learning
algorithms for reducing uncertainty in problem parameters (e.g. job execution
times, memory requirements, etc.) via prediction. However, only few studies
evaluate the impact of such techniques on the performances of the resource
manager.

@@

Parallel job scheduling is a old studied theoretical
problem~\cite{Frachtenberg:2009:JSS:1692356,Feitelson:2004:PJS:2128864.2128865}
whose practical ramifications, varying hypotheses, and inherent uncertainty of
the problem applied to the HPC field have driven practitioners to use simple
heuristics (and researchers to study their behavior). The two most popular
heuristics for HPC platforms are EASY~\cite{easy} and
Conservative~\cite{Mu'alem:2001:UPW:380314.380315} backfillings.

@@

The dynP scheduler~\cite{streit_selftuning_2002} proposes a systematic
method to tunine these queues, although it requires simulated scheduling runs
at decision time and therefore, it costs much more than the natural execution of EASY.

@@

There was a recent focus on leveraging the huge amount of data available in
large scale computing platforms in order to improve system performance. Some
works use collaborative filtering to colocate tasks in clouds by estimating
application interference~\cite{7516031}. Some others are closer to the
application level. For instance, ~\cite{fmodeling} uses binary classification
to distinguish benign memory faults from application errors in order to execute
recovery algorithms.

@@

The selection of the job to run is performed according to a scheduling policy,
which determines the order in which the jobs are executed. EASY-Backfilling is
the most widely used policy due to its simple and robust implementation and
known benefits such as high system utilization~\cite{easy}. This strategy has
no worst case guarantee beyond the absence of starvation (i.e. every job will
be scheduled at some moment).

The EASY-FCFS heuristic uses a job queue to select and backfill jobs.  At any
time requiring a scheduling decision (i.e. job submission or termination),
the scheduler goes through the job queue in First-Come,First-Serve (FCFS) order
and starts jobs until it finds a job that can not be started right away. Then,
it makes a reservation for this job at the earliest predictable time and
starts \textit{backfilling} the job queue in FCFS order, starting any job that
does not delay the unique reservation.

@@

We further assume that there is a certain regularity among periods,
\textit{i.e.} that the distribution of the job submission process does not
radically differ between consecutive periods. This assumption is validated in
the study presented in~\cite{jsspp17}. It further entails that the behavior of
a policy on the previous periods reflects its behavior on the current one, so
that the selection of a policy can be based on its behavior on previous
periods. However, there may be some variability between different periods for
certain cost metrics~\cite{feitelson2001metrics}. This is illustrated in
Figure~\ref{fig:mosn} which displays the average waiting time of various
policies for the KTH-SP2 trace (see~\ref{sub:traces} for a description of the
workloads) using weekly periods encompassing one year. As one can note, the
average waiting time varies a lot from one week to the other, for all the 7
policies considered. This indicates that when when the cost metric is averaged
over different periods, there is a tradeoff to find in between longer periods
that would somehow limit the variability, and shorter ones that yield more
values for the estimation. We will come back to this issue below.

@@

Thus, we explore here a more efficient strategy that dispenses with estimating
the cost of all policies at a given time and only updates the cost of the
policy that is currently being used. This strategy makes use of the
$\epsilon$-greedy exploration method, standard in reinforcement learning
\cite{Watkins:1989} and bandit problems~\cite{Auer2002}, to tradeoff
exploitation and exploration, and relies, as before, on past estimates of the
cost to select the best policy in the exploitation mode.

@@

Several studies propose to decay $\epsilon$ over time, the exploration being
less important once the estimates for the different policies are reliable
\cite{Tokic:2010}. This strategy has however not been beneficial in our case.
We believe this is due to the properties of the traces we use, as explained in
Section~\ref{sec:experiments}. The $\epsilon$-greedy strategy is known to be
outperformed in terms of regret by other classical algorithms such as the UCB
or EXP family of algorithms. See~\cite{bubnow} for a precise definition and
thourough treatment of this subject. These algorithms however all rely on
pre-normalized rewards. Here, the scale of $w_{\epsilon}(t;P_i)$ is not known
in advance. While the usual doubling tricks can be devised to go around
sequential issues of scale with good asymptotical performance, they ruin
performance in practice. Accordingly, we only perform experiments using the
simple $\epsilon$-greedy method.

@@

The choice of a simulator is a critical part of experimental validation that
raises a tradeoff between precision and runtime. High precision can be obtained
by carefully modeling the platform and its network topology, or extracting
information from the jobs from their sources or post-morted logs. This is the
approach used by high-fidelity batch scheduling simulators such as
Batsim~\cite{batsim}. In the present work, the focus is on studying the
EASY-Backfilling mechanism in itself, without adressing the allocation problem.
Moreover, the experimental protocol used here requires many simulation runs.
Therefore, we set the precision/runtime tradeoff at the point which minimizes
simulation runtimes. We discard all topological information relative to the
platform and use the job processing times of the original workloads. In this
setup, the processors are considered to be undistinguishable from each other,
and jobs can be discontinuously mapped to any available processor on the
system. We develop a lightweight simulator\cite{ocst} and release it to the
community. See the reproducibility paragraph below for more information.  With
this simulator, we are able to replay EASY-FCFS on the CEA-CURIE trace in 33
seconds with a machine equipped with an Intel(R) Core(TM) i5-4310U CPU @
2.00GHz. As a comparison, the Batsim simulator with network
communication modeling disabled and no resource contiguity takes more than 7 hours to
replay the same trace on the same hardware. The complete simulation campaign
presented below is executed on a single Dell PowerEdge R730 in 22 hours,
including input preparation and analysis code.

@@

Comparing algorithms in batch scheduling is made especially difficult by the
fluctuations in commonly used metrics~\cite{jsm}. The variability in
performance is known to outrank the available sample sizes: \textit{It is not
enough to simply replay an algorithm using a workload trace}. Indeed, as
presented in Figure~\ref{fig:variability}, the objective function we are using
in this work is subject to high variability. This variability can be so extreme
that even a timeframe of a fews years can be insufficient to compare scheduling
algorithms. In our experience inverting some months in the trace at random can
lead to reversal in the results. This motivated decades of research in workload
modeling~\cite{feitbook}. A recent approach~\cite{feitresampling} proposes to
resample data directly from the original traces. In this work, we use a simple
implementation of these ideas.  More precisely, we want to sample the job
submission process, which is achieved in the following manner: For evey week in
a resampled trace, we iterate over every existing user in the original trace.
For each of these users, we choose a week of the original trace uniformly at
random. The jobs from this user in this original week are chosen to be present
in the week being resampled.  This simple mechanism enables us to preserve the
dependency within a week.  Although the system state may not be independent
from one week to an other, we rely on existing work~\cite{jsspp17} and assume
for these experiments that the system is in a stationary state. While we
do provide guidelines as how to incorporate tracking variant of our algorithms
in Section~\ref{sec:online} by introducing a decaying discount factor $\lambda$,
this will not be studied in the experiments from this paper, and is left for
future research.

@@

  \item The simulation-based ("full feedback") strategy with hyperparameter
    $\Delta \in \left\{ 1 \text{day},1 \text{week} \right\}$. This choice of
    hyperparameter is a consequence of the natural rythm of human activity:
    daily or weekly simulation periods seem to facilitate comparability of
    performance between two periods. Indeed, arbitrary period values would
    needlessly increase the variability of the cost metric.

  \item The noisy simulation ("noisy feedback") variant with hyperparameter
    $\Delta \in \left\{ 1 \text{day},1 \text{week} \right\}$.

  \item The bandit feedback strategy with hyperparameters $\lambda=1, \Delta
    \in \left\{ 1 \text{day},1 \text{week} \right\}$. The choice of $\lambda=1$
    means that we use no decay in the estimation of the overall cost. Choosing
    to eliminate decay in this experimental campaign is natural since our
    resampled data is in a stationary regime \textit{by construction}, as
    explained in~\ref{ssub:resampling}.

  \item An additional "Random" strategy to be used as a reference point, with
    hyperparameter $ \Delta \in \left\{ 1 \text{day},1 \text{week} \right\}$.
    This strategy corresponds to choosing $P_i$ uniformly at random in $\left\{
      P_1 , \cdots, P_{12} \right\}$ during every period $\Delta_t$.

@@

The best values are outlined in bold in the table. These values give the best
attainable performance in the search set defined in~\ref{subsec:policies}.
Note that there seems to be some regularity; the SAF policy is remarkably
inefficient for instance, and the LQF policy works very well. However, note
that there are traces for which LQF is not optimal. Moreover, these
are~\textit{a-posteriori} results, which means that we only know post-factum
that this policy would have been better. In the present work, we are
studying adaptive policies that obtain a good performance on any given system
by selecting one of these policies.

@@

Figure~\ref{fig:all} reports the evolution of the average cumulative waiting
time for the UniLu-Gaia tis quantityrace, which means that it shows how the
average improvement in cumulative waiting time evolves as a function of time.
In other words, this is the average curve obtained if one were to plot the
cumulative sum of job waiting times for every resampled trace, incrementing the
sum when a job finishes. Accordingly, the final values attained by every curve
correspond exactly to the values reported in Table~\ref{tab:full}. The dashed
values represent the 10th and 90th percentile of the values.

Observe that while the 10th and 90th percentiles of the improvement with
respect to EASY-FCFS are large, the values are still contained enough to make
definite statements about how these policies compare to the FCFS baseline.
This figure does not report the variability of the policies against one another,
and does not allow to compare them beyong comparing their average performance.
However, the fact that the band of percentiles are roughly of the size of half
the best attainable improvement was our original motivation for this work, as
one can expect to be able to distinguish between these policies in an
online manner.

@@

This approach was used in two methods: a method based on a simulator and a
method based on a multi-armed bandit algorithm. The first one provides very
good results, reducing the average waiting times of the baseline FCFS ordering
policy by 11\% to 60\%. The second one is slighly less efficient with an
improvement factor of 8\% to 46\%. However, it is easier to use and cheaper
to run.

@@

This appendix describes the computational artifacts associated with this work. We
take a lightweight approach to replicability by packaging a declarative
workflow that generates all the figures from this paper and making it available
publicly. Moreover, questions regarding replication can be freely directed at
the authors via e-mail.

@@

There are various approaches for making computational experiments replicable,
among which distributing complete operating system images, containers, or
packaging software. As our experiments are cpu bound, we decide to opt for the
software packaging approach. This allows for replicating the experiments on clusters where virtualization is not
available or kernels are too old for containers old and decreases runtime.

@@

{\small
\begin{itemize}
  \item {\bf algorithm: Scheduling Simulation Workflow}
  \item {\bf program: Ocaml, R, Bash, Zymake(all sources and dependencies included)}
  \item {\bf compilation: Ocaml 4.02.3, GNU bash version 4.4.5(1)-release, R version 3.3.2}
  \item {\bf transformations: Patched nix standard environment.}
  \item {\bf binary: Most binaries are cached by Nix channels.}
  \item {\bf data set: Traces from the parallel workload archive, included.}
  \item {\bf run-time environment: Nixpkgs 17.03}
  \item {\bf hardware: Dell PowerEdge R730}
  \item {\bf output: Files}
  \item {\bf experiment workflow: \lstinline[basicstyle=\ttfamily\color{blue}]|zymakefile|, see below}
  \item {\bf publicly available?: Open-Sourced under the ISC~\cite{isc} license.}
\end{itemize}
}

@@

The archive containing the experimental workflow can be obtained at
\url{(omitted due to double-blind review)} Running the experiments can be done
on any platform equipped with the nix package manager by running at the root of
the extracted archive:

@@

 The experiments in this paper can run via in less than 24 hours on a
 moderately parallel host. More precisely, we had access to a Dell PowerEdge
 R730 equipped with a total of 56 threads @2.4GHz each and 757G of RAM. For
 this reason, the experimental campaign workflow was designed to be executed on
 a single host.

@@

All the software dependencies of our experiments are automatically managed by Nix.
The Nix software is available at \url{https://nixos.org/nix}.

@@

All data from this paper was obtained from the Swf Parallel Workloads
Archive~\cite{Feitelson20142967}. The data is cached in gzipped format in the
persistent archive associated with this workflow, should the Parallel
Workdloads Archive become unavailable.

@@

The experiment dependencies are loaded into the environment by the
\lstinline[basicstyle=\ttfamily]|nix-build| command.

@@

 All experiments are tied together using zymake~\cite{zymake}, a minimalistic
 workflow system designed for computational experiments\footnote{the zymake system
 is also packaged by our nix expressions.}. This system is
 analogous to a traditional build system with added workflow capabilities. The
 entire workflow that generates this article from the input data is contained
 in a single \lstinline[basicstyle=\ttfamily\color{blue}]|zymakefile| to be
 found at the root of the main archive. This workflow is composed of the
 following steps:

 \begin{itemize}
   \item[data]: Data extraction from archives, filtering, resampling.
     this is principally using shell scripts for data manipulation (see file
     \lstinline[basicstyle=\ttfamily\color{blue}]|misc/strong\_filter| for the
     filtering steps used) and ocaml code that implements the resampling method
     described in~\ref{ssub:resampling}.

@@

Readers interested with modifying the experiments can obtain the zenodo archive
at \url{https://truc.tgz}

The experiments are replicated with the same procedure as before, this time
invoking the build command with the local folder:

@@

>>>>

Providing the computing infrastuctures needed to solve actual complex problems
arising in the various fields of modern society (including climate change,
health, green energy or security) is a strategic challenge. The main pillar of
the answer to this challenge is to build extreme-scale parallel and distributed
platforms. The never-ending race for more computing power and storage capacity
does not only lead to sophisticated specific Exascale platforms, but the
objective of the community is to design efficient sustained Petascale
platforms. This large-scale evolution and the increasing complexity in both
architecture and applications create many scientific and technical problems.
Accordingly, system management software still has a long way to go. The
existing job and resource management software allow to run tens of thousands of
jobs on hundreds of thousands of cores. These software are based on robust
policies with positive properties such as relative simplicity and prevention of
job starvation. However, there is still room for improvement. Here, we propose
to study how to tune the ordering of the submission queues in the frame of the
classical EASY-BackFilling family of heuristics using two new online approaches
(an approach based on a simulator and an approach using multi-armed bandit).

Most common work in the literature consider \textit{a posteriori} optimization
of a scheduling algorithm on a (actual) data set.  The increasing amount and
diversity of data generated by large scale platforms motivate the community to
study more sophisticated policies that could leverage these data.  During the
last few years, there was an explosion of the number of works at the interface
of HPC and BigData fields, dealing with learning algorithms. Recent
sophisticated approaches developed \textit{ad hoc} supervised machine learning
algorithms for reducing uncertainty in problem parameters (e.g.\ job execution
times, memory requirements, etc.). However, only few studies
evaluate the impact of such techniques on the performances of the resource
manager.

@@

Parallel job scheduling is a old studied theoretical
problem~\cite{Frachtenberg:2009:JSS:1692356,Feitelson:2004:PJS:2128864.2128865}
whose practical ramifications, varying hypotheses, and inherent uncertainty of
the problem applied to the HPC field have driven practitioners to use simple
heuristics (and researchers to study their behavior). The two most popular
heuristics for HPC platforms are EASY~\cite{easy} and
Conservative~\cite{Mu'alem:2001:UPW:380314.380315} backfilling.

@@

The dynP scheduler~\cite{streit_selftuning_2002} proposes a systematic
method to tuning these queues, although it requires simulated scheduling runs
at decision time and therefore, it costs much more than the natural execution of EASY.

@@

There was a recent focus on leveraging the huge amount of data available in
large scale computing platforms in order to improve system performance. Some
works use collaborative filtering to co-locate tasks in clouds by estimating
application interference~\cite{7516031}. Some others are closer to the
application level. For instance, ~\cite{fmodeling} uses binary classification
to distinguish benign memory faults from application errors in order to execute
recovery algorithms.

@@

The selection of the job to run is performed according to a scheduling policy,
which determines the order in which the jobs are executed. EASY-Backfilling is
the most widely used policy due to its simple and robust implementation and
known benefits such as high system utilization~\cite{easy}. This strategy has
no worst case guarantee beyond the absence of starvation (i.e.\ every job will
be scheduled at some moment).

The EASY-FCFS heuristic uses a job queue to select and backfill jobs.  At any
time requiring a scheduling decision (i.e.\ job submission or termination),
the scheduler goes through the job queue in First-Come,First-Serve (FCFS) order
and starts jobs until it finds a job that can not be started right away. Then,
it makes a reservation for this job at the earliest predictable time and
starts \textit{backfilling} the job queue in FCFS order, starting any job that
does not delay the unique reservation.

@@

We further assume that there is a certain regularity among periods,
i.e.\ that the distribution of the job submission process does not
radically differ between consecutive periods. This assumption is validated in
the study presented in~\cite{jsspp17}. It further entails that the behavior of
a policy on the previous periods reflects its behavior on the current one, so
that the selection of a policy can be based on its behavior on previous
periods. However, there may be some variability between different periods for
certain cost metrics~\cite{feitelson2001metrics}. This is illustrated in
Figure~\ref{fig:mosn} which displays the average waiting time of various
policies for the KTH-SP2 trace (see~\ref{sub:traces} for a description of the
workloads) using weekly periods encompassing one year. As one can note, the
average waiting time varies a lot from one week to the other, for all the 7
policies considered. This indicates that when when the cost metric is averaged
over different periods, there is a trade-off to find in between longer periods
that would somehow limit the variability, and shorter ones that yield more
values for the estimation. We will come back to this issue below.

@@

Thus, we explore here a more efficient strategy that dispenses with estimating
the cost of all policies at a given time and only updates the cost of the
policy that is currently being used. This strategy makes use of the
$\epsilon$-greedy exploration method, standard in reinforcement learning
\cite{Watkins:1989} and bandit problems~\cite{Auer2002}, to trade-off
exploitation and exploration, and relies, as before, on past estimates of the
cost to select the best policy in the exploitation mode.

@@

Several studies propose to decay $\epsilon$ over time, the exploration being
less important once the estimates for the different policies are reliable
\cite{Tokic:2010}. This strategy has however not been beneficial in our case.
We believe this is due to the properties of the traces we use, as explained in
Section~\ref{sec:experiments}. The $\epsilon$-greedy strategy is known to be
outperformed in terms of regret by other classical algorithms such as the UCB
or EXP family of algorithms. See~\cite{bubnow} for a precise definition and
thorough treatment of this subject. These algorithms however all rely on
pre-normalized rewards. Here, the scale of $w_{\epsilon}(t;P_i)$ is not known
in advance. While the usual doubling tricks can be devised to go around
sequential issues of scale with good asymptotical performance, they ruin
performance in practice. Accordingly, we only perform experiments using the
simple $\epsilon$-greedy method.

@@

The choice of a simulator is a critical part of experimental validation that
raises a trade-off between precision and runtime. High precision can be obtained
by carefully modeling the platform and its network topology, or extracting
information from the jobs from their sources or post-mortem logs. This is the
approach used by high-fidelity batch scheduling simulators such as
Batsim~\cite{batsim}. In the present work, the focus is on studying the
EASY-Backfilling mechanism in itself, without addressing the allocation problem.
Moreover, the experimental protocol used here requires many simulation runs.
Therefore, we set the precision/runtime trade-off at the point which minimizes
simulation runtimes. We discard all topological information relative to the
platform and use the job processing times of the original workloads. In this
setup, the processors are considered to be undistinguishable from each other,
and jobs can be discontinuously mapped to any available processor on the
system. We develop a lightweight simulator\cite{ocst} and release it to the
community. See the reproducibility paragraph below for more information.  With
this simulator, we are able to replay EASY-FCFS on the CEA-CURIE trace in 33
seconds with a machine equipped with an Intel(R) Core(TM) i5-4310U CPU @
2.00GHz. As a comparison, the Batsim simulator with network
communication modeling disabled and no resource contiguity takes more than 7 hours to
replay the same trace on the same hardware. The complete simulation campaign
presented below is executed on a single Dell PowerEdge R730 in 22 hours,
including input preparation and analysis code.

@@

Comparing algorithms in batch scheduling is made especially difficult by the
fluctuations in commonly used metrics~\cite{jsm}. The variability in
performance is known to outrank the available sample sizes: \textit{It is not
enough to simply replay an algorithm using a workload trace}. Indeed, as
presented in Figure~\ref{fig:variability}, the objective function we are using
in this work is subject to high variability. This variability can be so extreme
that even a time-frame of a fews years can be insufficient to compare scheduling
algorithms. In our experience inverting some months in the trace at random can
lead to reversal in the results. This motivated decades of research in workload
modeling~\cite{feitbook}. A recent approach~\cite{feitresampling} proposes to
resample data directly from the original traces. In this work, we use a simple
implementation of these ideas.  More precisely, we want to sample the job
submission process, which is achieved in the following manner: For every week in
a resampled trace, we iterate over every existing user in the original trace.
For each of these users, we choose a week of the original trace uniformly at
random. The jobs from this user in this original week are chosen to be present
in the week being resampled.  This simple mechanism enables us to preserve the
dependency within a week.  Although the system state may not be independent
from one week to an other, we rely on existing work~\cite{jsspp17} and assume
for these experiments that the system is in a stationary state. While we
do provide guidelines as how to incorporate tracking variant of our algorithms
in Section~\ref{sec:online} by introducing a decaying discount factor $\lambda$,
this will not be studied in the experiments from this paper, and is left for
future research.

@@

  \item The simulation-based ("full feedback") strategy with hyper-parameter
    $\Delta \in \left\{ 1 \text{day},1 \text{week} \right\}$. This choice of
    hyper-parameter is a consequence of the natural rhythm of human activity:
    daily or weekly simulation periods seem to facilitate comparability of
    performance between two periods. Indeed, arbitrary period values would
    needlessly increase the variability of the cost metric.

  \item The noisy simulation ("noisy feedback") variant with hyper-parameter
    $\Delta \in \left\{ 1 \text{day},1 \text{week} \right\}$.

  \item The bandit feedback strategy with hyper-parameters $\lambda=1, \Delta
    \in \left\{ 1 \text{day},1 \text{week} \right\}$. The choice of $\lambda=1$
    means that we use no decay in the estimation of the overall cost. Choosing
    to eliminate decay in this experimental campaign is natural since our
    resampled data is in a stationary regime \textit{by construction}, as
    explained in~\ref{ssub:resampling}.

  \item An additional "Random" strategy to be used as a reference point, with
    hyper-parameter $ \Delta \in \left\{ 1 \text{day},1 \text{week} \right\}$.
    This strategy corresponds to choosing $P_i$ uniformly at random in $\left\{
      P_1 , \cdots, P_{12} \right\}$ during every period $\Delta_t$.

@@

The best values are outlined in bold in the table. These values give the best
attainable performance in the search set defined in~\ref{subsec:policies}.
Note that there seems to be some regularity; the SAF policy is remarkably
inefficient for instance, and the LQF policy works very well. However, note
that there are traces for which LQF is not optimal. Moreover, these
are~\textit{a-posteriori} results, which means that we only know
textit{post-factum} that this policy would have been better. In the present
work, we are studying adaptive policies that obtain a good performance on any
given system by selecting one of these policies.

@@

Figure~\ref{fig:all} reports the evolution of the average cumulative waiting
time for the UniLu-Gaia, which means that it shows how the
average improvement in cumulative waiting time evolves as a function of time.
In other words, this is the average curve obtained if one were to plot the
cumulative sum of job waiting times for every resampled trace, incrementing the
sum when a job finishes. Accordingly, the final values attained by every curve
correspond exactly to the values reported in Table~\ref{tab:full}. The dashed
values represent the 10th and 90th percentile of the values.

Observe that while the 10th and 90th percentiles of the improvement with
respect to EASY-FCFS are large, the values are still contained enough to make
definite statements about how these policies compare to the FCFS baseline.
This figure does not report the variability of the policies against one another,
and does not allow to compare them beyond comparing their average performance.
However, the fact that the band of percentiles are roughly of the size of half
the best attainable improvement was our original motivation for this work, as
one can expect to be able to distinguish between these policies in an
online manner.

@@

This approach was used in two methods: a method based on a simulator and a
method based on a multi-armed bandit algorithm. The first one provides very
good results, reducing the average waiting times of the baseline FCFS ordering
policy by 11\% to 60\%. The second one is slightly less efficient with an
improvement factor of 8\% to 46\%. However, it is easier to use and cheaper
to run.

@@

This appendix describes the computational artifacts associated with this work.
We take a lightweight approach to replicability by packaging and publishing a
declarative workflow that generates all the figures from this paper. Moreover,
questions regarding replication can be freely directed to the authors via
e-mail.

@@

There are various approaches for making computational experiments replicable,
among which distributing complete operating system images, containers, or
packaging software. As our experiments are CPU bound, we decide to opt for the
software packaging approach. This allows for replicating the experiments on
clusters where virtualization is not available or kernels are too old for
containers and decreases simulation runtime.

@@

{\small
\begin{itemize}
  \item {\bf Algorithm: Scheduling Simulation Workflow}
  \item {\bf Program: Ocaml, R, Bash, Zymake(all sources and dependencies included)}
  \item {\bf Compilation: Ocaml 4.02.3, GNU bash version 4.4.5(1)-release, R version 3.3.2}
  \item {\bf Transformations: Patched nix standard environment.}
  \item {\bf Binary: Most binaries are cached by Nix channels.}
  \item {\bf Data set: Traces from the parallel workload archive, included.}
  \item {\bf Run-time environment: Nixpkgs 17.03}
  \item {\bf Hardware: Dell PowerEdge R730}
  \item {\bf Output: Files}
  \item {\bf Experiment workflow: \lstinline[basicstyle=\ttfamily\color{blue}]|zymakefile|, see below}
  \item {\bf Publicly available?: Open-Sourced under the ISC~\cite{isc} license.}
\end{itemize}
}

@@

The archive containing the experimental workflow can be obtained at
(URL omitted due to double-blind review). Running the experiments can be done
on any platform equipped with the nix package manager by running at the root of
the extracted archive:

@@

 The experiments in this paper can run in less than 24 hours on a
 moderately parallel host. More precisely, we had access to a Dell PowerEdge
 R730 equipped with a total of 56 threads @2.4GHz each and 757 Gigabites of RAM. For
 this reason, the experimental campaign workflow was designed to be executed on
 a single host.

@@

All the software dependencies of our experiments are automatically managed by Nix.
The Nix package manager is available at \url{https://nixos.org/nix}.

@@

All data from this paper were obtained from the Swf Parallel Workloads
Archive~\cite{Feitelson20142967}. The data is cached in gzipped format in the
persistent archive associated with this workflow, should the Parallel
Workloads Archive become unavailable.

@@

The experiment's dependencies are loaded into the environment by the
\lstinline[basicstyle=\ttfamily]|nix-build| command.

@@

 All experiments are tied together using zymake~\cite{zymake}, a minimalistic
 workflow system designed for computational experiments\footnote{The zymake system
 is also packaged by our nix expressions.}. This system is
 analogous to a traditional build system with added workflow capabilities. The
 entire workflow that generates this article from the input data is contained
 in a single \lstinline[basicstyle=\ttfamily\color{blue}]|zymakefile| to be
 found at the root of the main archive. This workflow is composed of the
 following steps:

 \begin{itemize}
   \item[data]: Data extraction from archives, filtering, resampling.
     this is principally using shell scripts for data manipulation (see file
     \lstinline[basicstyle=\ttfamily\color{blue}]|misc/strong_filter| for the
     filtering steps used) and ocaml code that implements the resampling method
     described in~\ref{ssub:resampling}.

@@

Readers interested in modifying the experiments can obtain the zenodo archive
at (URL omitted due to peer review).

@@

The experiments can then be run as before via:

Additionally, the experiments can be launched manually via:

\begin{lstlisting}
nix-shell -A banditSelection
zymake -l localhost zymakefile
\end{lstlisting}
